---
title: "Fewer inputs analyses"
output: html_notebook
---

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(grid)
library(gtable)
library(latex2exp)
```

```{r}
theme_set(theme_bw(base_size = 15) +
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
```



```{r}
nruns = 10
num_exampless = c(seq(10, 100, 10))#, 200, 400, 800)
noise_vars = c(1.)
output_sizes = c(100)
input_sizes= c(100)
svms = 1:8
input_types = c("orthogonal", "gaussian")
d = data.frame()
for (noise_var in noise_vars) {
  for (output_size in output_sizes) {
    for (input_size in input_sizes) {
      for (num_examples in num_exampless) {
        for (input_type in input_types) {
          for (svm in svms) {
            for (aligned in c("False")) {
              for (run in 0:(nruns-1)) { 
                this_d = read.csv(sprintf("../p_diff_results/noise_var_%.2f_output_size_%i_input_size_%i_num_examples_%i_input_type_%s_svm_%f_aligned_%s_run_%i.csv", noise_var, output_size, input_size, num_examples, input_type, svm, aligned, run), header=T)
                this_d = this_d %>% 
                  mutate(noise_var=noise_var, output_size=output_size, run=run, input_type=input_type, input_size=input_size, num_examples=num_examples, aligned=aligned, svm=svm, type="empirical")
                d = bind_rows(d, this_d)
              }
              if (file.exists(sprintf("../p_diff_results/noise_var_%.2f_p_%i_svm_%f_theory_track.csv", noise_var, num_examples, svm))) {
                this_d = read.csv(sprintf("../p_diff_results/noise_var_%.2f_p_%i_svm_%f_theory_track.csv", noise_var, num_examples, svm), header=T)
                this_d = this_d %>% 
                  rename(loss=generalization_error, train_loss=train_error) %>%
                  mutate(noise_var=noise_var, output_size=output_size, run=NA, input_type=input_type, input_size=input_size, num_examples=num_examples, aligned=aligned, svm=svm, type="theory")
                d = bind_rows(d, this_d)
              }
              
            }
          }
        }
      }
    }
  }
}
```

```{r}
d = d %>%
  mutate(output_size=factor(output_size),
         input_size=factor(input_size),
         sigma_z=(sqrt(noise_var)),
         SNR=svm/sigma_z,
         input_type=factor(input_type),
         noise_var=factor(noise_var),
         log_loss = log(loss))
```

```{r}
avg_d = d %>%
  group_by(SNR, svm, type, input_size, output_size, num_examples, epoch, input_type) %>%
  summarize(loss=mean(loss), log_loss_sd=sd(log_loss), log_loss=mean(log_loss)) %>%
  mutate(log_loss_95_low=log_loss-1.96*log_loss_sd/sqrt(n()), log_loss_95_high=log_loss+1.96*log_loss_sd/sqrt(n())) %>%
  ungroup() 
```


# P <= N_1
```{r}
ggplot(avg_d %>% filter(epoch %% 100 == 0, num_examples %in% c(10, 50, 100), type=="empirical"), aes(x=(epoch/1000), y=log_loss, color=SNR, shape=input_type, group=interaction(factor(SNR), input_type))) +
  geom_point(size=1.5) +
  geom_line(data=avg_d %>% filter(num_examples %in% c(10, 50, 100), type=="theory")) +
  scale_color_gradient(low="#0000FF", high="#FF0000") + 
#  geom_ribbon(aes(ymin=log_loss_95_low, ymax=log_loss_95_high, fill=features), alpha=0.5) +
  labs(x=TeX("$t/\\tau$"), y=TeX("$\\ln\\, \\epsilon_{test}$")) +
  guides(color=guide_colorbar(title="SNR"), shape=guide_legend(title="Input type")) +
  facet_grid(input_type~ num_examples)
```

```{r}
ggsave("../plots/p_less.png", width=6, height=4)
```

```{r}
min_d = d %>%
  unite(this_type, input_type, type,  sep=".") %>%
  group_by(SNR, svm, input_size, output_size, num_examples, this_type, run) %>%
  summarize(min_loss=min(loss)) %>%
  ungroup() %>%
  group_by(SNR, svm, input_size, output_size, num_examples, this_type) %>%
  summarize(se_ml=sd(min_loss)/sqrt(n()),
            min_loss=mean(min_loss),
            ml_ci_low=min_loss-1.96*se_ml,
            ml_ci_hi=min_loss+1.96*se_ml) %>%
  ungroup() %>%
  select(-se_ml) %>%
  gather(statistic, value, min_loss, ml_ci_low, ml_ci_hi) %>%
  unite(blah, this_type, statistic, sep=".") %>%
  spread(blah, value) %>%
  gather(measurement, value, gaussian.empirical.min_loss:orthogonal.theory.ml_ci_low) %>%
  separate(measurement, c("input_type", "theory_or_empirical", "metric"), sep="\\.") %>%
  spread(metric, value)
```

```{r}
#ggplot(data=min_d, aes(x=orthogonal_min_loss, y=gaussian_min_loss, color=SNR)) +
#  scale_color_gradient(low="#0000FF", high="#FF0000", limits=c(1, 10), breaks=c(1, 10))  +
#  geom_abline(aes(intercept=0, slope=1), alpha=0.5, linetype=3) +
#  geom_errorbar(aes(ymin=gaussian_ml_ci_low, ymax=gaussian_ml_ci_hi)) +
#  geom_errorbarh(aes(xmin=orthogonal_ml_ci_low, xmax=orthogonal_ml_ci_hi)) +
#  labs(x="Min log generalization error (Orthogonal)",
#       y="Min log generalization error (Gaussian)") +
#  geom_point(size=2) +
#  facet_wrap( ~ num_examples)
```

```{r}
#ggsave("../plots/p_less_min_gens.png")
```


```{r}
ggplot(avg_d %>% filter(epoch %% 100 == 0,  num_examples >= 100, type=="empirical"), aes(x=ifelse(type=="theory", sqrt(100/num_examples) *epoch/1000, epoch/1000), y=log_loss, color=SNR, shape=input_type, group=interaction(factor(SNR), input_type))) +
  geom_point(size=1.5) +
  geom_line(data=avg_d %>% filter( num_examples >= 100, type=="theory")) +
  scale_color_gradient(low="#0000FF", high="#FF0000") + 
#  geom_ribbon(aes(ymin=log_loss_95_low, ymax=log_loss_95_high, fill=features), alpha=0.5) +
  labs(x=TeX("$t/\\tau$"), y=TeX("$\\ln\\, \\epsilon_{test}$")) +
  guides(color=guide_colorbar(title="SNR"), shape=guide_legend(title="Input type")) +
  facet_grid(input_type~ num_examples)
```

```{r}
ggsave("../plots/p_greater.png", width=8, height=4)
```

```{r}
ggplot(data=min_d %>% filter(theory_or_empirical == "empirical"), aes(x=log(num_examples/100), y=min_loss, color=input_type, shape=input_type)) +
#  geom_errorbar(aes(ymin=gaussian_ml_ci_low, ymax=gaussian_ml_ci_hi), width=10) +
  labs(x="Log P/N_1",
       y="Min log generalization error (Gaussian)") +
  geom_point(size=3) +
  geom_line(data=min_d %>% filter(theory_or_empirical == "theory", input_type=="orthogonal"), aes(shape=NA, color=NA, group=SNR), color="black", size=1.2) +
  facet_wrap(~ SNR)
```

```{r}
ggsave("../plots/min_gen_comparison.png", width=7, height=5)
```

```{r}
ggplot(data=min_d %>% filter(theory_or_empirical == "empirical", num_examples <= 100, input_type=="orthogonal"), aes(x=(num_examples/100), y=SNR, fill=min_loss)) + 
  geom_tile() +
  labs(x="P/N1", y="SNR") +
  guides(fill=guide_colorbar(title=TeX("$\\min \\, \\ln\\, \\epsilon_{test}$")))
```


```{r}
ggsave("../plots/min_gen_heatmap.png", width=7, height=5)
```